Um \textit{Framework} de Desenvolvimento de Aplicações Ubíquas em Ambientes Inteligentes

### 2012-12-03 trunk/ labtempo-ubicomp-projects/UbicompMiddleware/doc/sbrc-2013-dm/ubicomp-middleware.tex
Revisão de resumo e tabela

%%%%%%%%%%%%%%
%  RESUMOS   %
%%%%%%%%%%%%%%
\begin{abstract}
With recent advances in mobile computing and wireless communication technologies, we can see the emergence of a favorable construction of ubiquitous applications. This paper proposes a new framework for building such applications, providing a conceptual and implementation tools. We propose abstractions that allow developers to handle the resources distributed in the environment in a simple and homogeneous, and interpret the context information. In order to demonstrate the feasibility of the proposal, the concepts were implemented in a platform called SmartAndroid. This platform also includes an interface prototyping applications ubiquitous environments where settings can be tested before the acquisition of all devices, and interface composition of contextual rules, where end users can set preferences on the environment.
\end{abstract}

@@

%((((((((((((((((((((((((((((tabela 1))))))))))))))))))))))))))))))
\begin{table} % aqui começa o ambiente tabela
\centering
\caption{Operações do SGAR} % igual ao ambiente figura
\begin{tabular}{|c|c|p{2.6cm}|p{6.1cm}|} 
\hline % este comando coloca uma linha na tabela
Serviço & Operação & Argumentos & Descrição\\ 
\hline
SRR & \textit{register} & Dados do AR & Insere dados do AR no Repositório  \\ \hline
SRR & \textit{unregister} & Dados do AR & Remove AR do Repositório  \\ \hline
SDR & \textit{search} & Consulta & Busca ARs por tipo, local ou nome   \\ \hline
SLR & \textit{getPlaces} & Nenhum & Retorna a lista de espaços do Mapa \\ \hline
SLR & \textit{searchByProximity} & Posição & Retorna ARs mais próximos \\ \hline
AR & \textit{subscribe} & AR e VC & Adiciona interesse do AR no VC \\ \hline
AR & \textit{publish} & VC e Valor & Notifica ARs interessados no VC \\ \hline
\end{tabular}
\label{tab:api}
\end{table}

>>>>

%%%%%%%%%%%%%%
%  RESUMOS   %
%%%%%%%%%%%%%%
\begin{abstract}
With recent advances in mobile computing and wireless communication technologies, we can see the emergence of a favorable construction of ubiquitous applications. This paper proposes a new framework for building such applications, providing a conceptual and implementation tools. We propose abstractions that allow developers to handle the resources distributed in the environment and interpret the context informationin in a simple and homogeneous way. In order to demonstrate the feasibility of the proposal, the concepts were implemented in a platform called SmartAndroid. This platform also includes an prototyping interface for ubiquitous applications, where settings can be tested before the acquisition of all devices, and interface composition of contextual rules, where end users can set preferences on the environment.
\end{abstract}

@@

%((((((((((((((((((((((((((((tabela 1))))))))))))))))))))))))))))))
\begin{table} % aqui começa o ambiente tabela
\centering
\caption{Operações do SGAR} % igual ao ambiente figura
\begin{tabular}{|c|c|p{2.6cm}|p{6.1cm}|} 
\hline % este comando coloca uma linha na tabela
Serviço & Operação & Argumentos & Descrição\\ 
\hline
SRR & \textit{register} & Dados do AR & Insere dados do AR no Repositório  \\ \hline
SRR & \textit{unregister} & Dados do AR & Remove AR do Repositório  \\ \hline
SDR & \textit{search} & Consulta & Busca ARs por tipo, local e/ou nome   \\ \hline
SLR & \textit{getPlaces} & Nenhum & Retorna a lista de espaços do Mapa \\ \hline
SLR & \textit{searchByProximity} & Posição & Retorna ARs mais próximos \\ \hline
AR & \textit{subscribe} & AR e VC & Adiciona interesse do AR no VC \\ \hline
AR & \textit{publish} & VC e Valor & Notifica ARs interessados no VC \\ \hline
\end{tabular}
\label{tab:api}
\end{table}
